Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-07 paper/ms.tex
Revert posterior dist of dx,dv and orbit figures.

@@

In a separate effort to study detailed chemical abundances of potential
planet-hosting stars, \citet{2016ApJS..225...32B} obtained and analyzed high resolution
spectra of both stars using the HIRES spectrograph on the Keck~I telescope.
The spectral resolution is $R\approx 70000$ and the wavelength coverage is
$5164--7799$~\AA.
A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar parameters
and high precision radial velocities.
For the details of the spectral analysis, we refer the readers to
\citealt{2016ApJS..225...32B}.
The \elem{Li} doublet at $6707.6$~\AA\ --- clearly visible in both spectra (see
\figname~\ref{fig:spec2}) --- for this sample was investigated in a separate
work (\citealt{jmlithium}).
We list all spectroscopic measurements including
the absolute abundance\footnote{
  Absolute abundance of element \elem{X} is
  $A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
  where $n_\elem{X}$ is the number density of element \elem{X}.
}
of \elem{Li} for the two stars in Table~\ref{tab:kk}.

Although selected based only on their astrometry, the two stars
have identical radial velocities within uncertainties (Table~\ref{tab:kk}),
confirming that they are truly comoving.
The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
and the 3D separation is $\approx 0.6$~pc.
% note on uncertainties
Given their proximity in phase space, it is generally accepted to assume that
the two stars were born together and, perhaps, are a bound wide binary system.
Thus, we expect the two stars to have identical metallicities and abundance patterns.
Surprisingly, one of the stars, \bizarreone\ is significantly more metal
rich than the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
Even more puzzling is that not all elements are equally enhanced:
the abundances of \bizarreone\ show selective depletion in
\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}
relative to \elem{Fe}.

@@

>>>>

Throughout the \documentname\, we use the following convention for
chemical abundances of stars: [\elemH{X}] is the ratio of number density of
element \elem{X} to \elem{H} relative to the solar values.
The absolute abundance of \elem{X} is
$A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
where $n_\elem{X}$ is the number density of element \elem{X}.

@@

In a separate effort to study detailed chemical abundances of potential
planet-hosting stars, \citet{2016ApJS..225...32B} obtained and analyzed high resolution
spectra of both stars using the HIRES spectrograph on the Keck~I telescope.
The spectral resolution is $R\approx 70000$ and the wavelength coverage is
$5164--7799$~\AA.
A typical signal-to-noise ratio in the spectral continuum is $>200$~per pixel.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar parameters
and high precision radial velocities.
For the details of the spectral analysis, we refer the readers to
\citealt{2016ApJS..225...32B}.
The \elem{Li} doublet at $6707.6$~\AA\ --- clearly visible in both spectra (see
\figname~\ref{fig:spec2}) --- for this sample was investigated in a separate
work (\citealt{jmlithium}).
We list all spectroscopic measurements including
the absolute abundance\footnote{
  The absolute abundance of element \elem{X} is
  $A(\elem{X}) = \log_{10} (n_\elem{X}/n_\elem{H})$
  where $n_\elem{X}$ is the number density of element \elem{X}.
}
of \elem{Li} for the two stars in Table~\ref{tab:kk}.

The projected separation between the pair is 1.9\arcmin\ ($\approx 0.01$~pc),
and the 3D separation is $\approx 0.6$~pc.
Although selected based only on their astrometry, the two stars
have identical radial velocities within uncertainties (Table~\ref{tab:kk}),
confirming that they are truly comoving.
Combining these precise radial velocities with the \gaia\ \tgas\ astrometry, we
can compare differences between the inferred 6D phase space coordinates of the
two stars.
We start by generating posterior samples over the Heliocentric distance, $r$,
tangential velocities, $(v_\alpha, v_\delta)$, and radial velocity, $\hat{v}_r$,
given the observed parallax, $\pi$, and proper motion components,
$(\mu_{\alpha^*}, \mu_\delta)$, and radial velocity, $v_r$.
By defining the vectors
% SMOH: I understand you meant hat v_r as the latent true radial velocity but
% personally think a) it can confuse some people that there are hat quantities
% with no-hat quantities for hat-y vector and thus b) it'd be better to use hat
% quantities for observed variables and no-hat for latent true ones.
% SMOH: v_r is missing in the LHS of eq(3)
\begin{eqnarray}
  \vec{y} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          \pi &
          \mu_{\alpha^*} &
          \mu_\delta &
          v_r
        \end{array}
      \right)}\\
  \hat{\vec{y}} &=&
      \transp{\left(
        \begin{array}{c@{\hspace{1em}} c@{\hspace{1em}} c@{\hspace{1em}} c}
          r^{-1} &
          r^{-1}\,v_\alpha &
          r^{-1}\,v_\delta &
          \hat{v}_r
        \end{array}
      \right)}
\end{eqnarray}
and by considering the covariance matrix $\mat{C}$ between the observed
quantities (provided by \tgas\ and extended to include the uncorrelated radial
velocity uncertainty), the likelihood can be written
\begin{eqnarray}
p(\pi, \mu_{\alpha^*}, \mu_\delta \given r, v_\alpha, v_\delta) &=&
  \left[\det\left(\frac{\mat{C}^{-1}}{2\pi}\right)\right]^{1/2} \,
    \exp \left[ -\frac{1}{2} \transp{\left(\vec{y} - \hat{\vec{y}} \right)} \,
    \mat{C}^{-1} \,
    \left(\vec{y} - \hat{\vec{y}} \right) \right] \label{eq:likefn} \quad .
\end{eqnarray}
We adopt a uniform space density prior for the distance and an isotropic
Gaussian for any velocity component, $v$, with a dispersion $\sigma_v=25~\kms$
\begin{eqnarray}
p(r) &=&
  \begin{cases}
    \frac{3}{r_{\rm lim}^3} \, r^2 & \text{if } 0 < r < r_{\rm lim}\\
    0              & \text{otherwise}
  \end{cases}\\
p(v) &=& \frac{1}{\sqrt{2\pi}\,\sigma_v} \,
  \exp\left[-\frac{1}{2} \, \frac{v^2}{\sigma_v^2} \right] \quad .
\end{eqnarray}
For each of the two stars, we use \project{emcee}
(\citealt{Foreman-Mackey:2013}) to generate posterior samples in $(r, v_\alpha,
v_\delta, \hat{v}_r)$ by running 64 walkers for 4608 steps and discarding the
first 512 steps as the burn-in period.
For each sample, we convert the heliocentric phase-space coordinates into
Galactocentric coordinates assuming the Sun's position and velocity are $x_\odot
= (-8.3, 0, 0)~{\rm kpc}$ and $v_\odot = (10, 244, 7.17)~\kms$ (\citealt{bovy,
etc.}).
\figurename~\ref{fig:dxdv} shows differences in posterior samples converted to
Galactocentric phase-space coordinates for the two stars.
In all components, the pair is consistent with being co-moving and close in
separation; the sky-projected separation of the two stars is $\approx$$0.01~\pc$
but the median 3-space separation is $\approx$$0.6~\pc$.

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{dx_dv_posterior.pdf}
  \end{center}
  \caption{%
    Differences in posterior samples over Galactocentric phase-space coordinates
    for the two stars \sunanalog\ and \bizarreone.
    \label{fig:dxdv}}
\end{figure}

Given their proximity in phase space, it is generally accepted to assume that
the two stars were born together and, perhaps, are a bound wide binary system.
Thus, we expect the two stars to have identical metallicities and abundance patterns.
Surprisingly, one of the stars, \bizarreone\ is significantly more metal
rich than the other (by 0.2~dex $\approx 60\%$; \figname~\ref{fig:abundances}).
Even more puzzling is that not all elements are equally enhanced:
the abundances of \bizarreone\ show selective depletion in
\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}
relative to \elem{Fe}.

@@

\figurename~\ref{fig:orbit} shows an orbit computed from the median posterior
sample over 6D phase-space coordinates for \sunanalog\ (black line), integrated
in a Milky Way-like gravitational potential (\cite{Gala:2017}). \todo{APW:
explain}
The Sun's orbit in this same Milky Way model is under-plotted for comparison
(grey line); the orbits of the stars in this pair have large scale-heights
relative to the Sun's orbit despite being young.

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{orbits.pdf}
  \end{center}
  \caption{%
    Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
    For \sunanalog\, the initial conditions are set to the median posterior
    sample over the inferred 6D phase-space coordinates.
    The orbits are computed by integrating backwards from the present-day
    positions for $2.5~{\rm Gyr}$ with a time-step of $0.5~{\rm Myr}$ using the
    Leapfrog integration scheme implemented in \project{Gala}
    (\citealt{Gala:2017}). \todo{APW: citation...}
\label{fig:orbit}}
\end{figure}
